A comparison of design-based and model-based approaches for spatial data.

### 2021-08-12 inst/SpatialDVM_Manuscript/SpatialDVM_Manuscript.Rmd
figure pdfs.

# mike chunk
combo_data <- purrr::map_df(files,
                            ~read_csv(.x) %>% mutate(filename = .x)) %>%
  separate(filename, into = c("junk", "junk2", "error_dep", "dist", "n", "location"),
           sep = "_") %>%
  select(-junk, -junk2)

# matt chunk
# combo_data <- purrr::map_df(files,
#                             ~read_csv(.x) %>% mutate(filename = .x)) %>%
#   separate(filename, into = c("junk", "error_dep", "dist", "n", "location"),
#            sep = "_") %>%
#   select(-junk)

@@

combo_data_grts <- combo_data %>% filter(approach %in% c("Design GRTS", "Model GRTS"))

dep_only <- combo_data_grts %>% filter(error_dep == "deperr")
dep_long <- dep_only %>%
  pivot_wider(names_from = approach, values_from = rmspe, sim) %>%
  mutate(perc = 100 * (`Design GRTS` - `Model GRTS`) / `Model GRTS`)

>>>>

# mike chunk
# Mike: see if this works. If so, delete one of the duplicates
combo_data <- purrr::map_df(files,
                            ~read_csv(.x) %>% mutate(filename = .x)) %>%
  mutate(filetemp = str_extract(filename, pattern = "sim_\\w+")) %>% 
  separate(filetemp, into = c("junk", "error_dep", "dist", "n", "location"),
           sep = "_") %>%
  select(-junk)

# combo_data <- purrr::map_df(files,
#                             ~read_csv(.x) %>% mutate(filename = .x)) %>%
#   separate(filename, into = c("junk", "junk2", "error_dep", "dist", "n", "location"),
#            sep = "_") %>%
#   select(-junk, -junk2)

# matt chunk
combo_data <- purrr::map_df(files,
                            ~read_csv(.x) %>% mutate(filename = .x)) %>%
  mutate(filetemp = str_extract(filename, pattern = "sim_\\w+")) %>% 
  separate(filetemp, into = c("junk", "error_dep", "dist", "n", "location"),
           sep = "_") %>%
  select(-junk)

@@

combo_data_grts <- combo_data %>% dplyr::filter(approach %in% c("Design GRTS", "Model GRTS"))

dep_only <- combo_data_grts %>% dplyr::filter(error_dep == "deperr")
dep_long <- dep_only %>%
  pivot_wider(names_from = approach, values_from = rmspe, sim) %>%
  mutate(perc = 100 * (`Design GRTS` - `Model GRTS`) / `Model GRTS`)
